---
title: "p8105_hw5_sk5152"
author: "Shuting Kang"
date: "2022-11-15"
output: github_document
---
## Problem 2

The homicide datasets in 50 large U.S. cities from Washington Post are loaded in this project. 
```{r}
#for loop (map are better actually)
library(tidyverse)
homicide<-read_csv("./data/homicide-data.csv")
head(homicide)
skimr::skim(homicide)
```
```{r}
homicide_CityState<- homicide%>%
  mutate(city_state=str_c(city,state,sep=","))
head(homicide_CityState)

```
The homicides dataset contained `r nrow(homicide)` observation and `r ncol(homicide)` variables. I excluded Tulsa, AL, because Tulsa,AL only have one record, which is consider as outlier.
```{r}
summary<-homicide_CityState%>%
  group_by(city_state)%>%
  summarize(
    total_cases=n(),
    solved=sum(disposition=="Closed by arrest"),
    unsolved=sum(disposition!="Closed by arrest")
  )%>%
  filter(city_state!="Tulsa,AL")
summary
```
For the city of Baltimore, MD, prop.test function was utilized to estimate the proportion of homicides that are unsolved. broom::tidy was applied to save the output of prop.test as an R object. The test method is 1-sample proportions test with continuity correction, the estimated proportion is 0.6455607, and the 95% confidence interval is (0.6275625,0.6631599)
```{r}
baltimore<-
  homicide_CityState%>%
  filter(city_state=="Baltimore,MD")%>%
  summarize(
    unsolved=sum(disposition!="Closed by arrest"),
    total_cases=n()
  )


baltimore_test <-prop.test(x=1825	,n=2827	)%>%
  broom::tidy()
baltimore_test
```

```{r}
result=
  summary%>%
  mutate(
    result=map2(unsolved,total_cases,prop.test),
    output_result=map(result, broom::tidy)
  )%>%
  unnest(output_result)%>%
  select(city_state,estimate,conf.low,conf.high)

result
```
I create a tidy dataframe with estimated proportions of CIs for each city based on the summary table, generated above, which contain city_state, the number of unsolved, solved, and total cases for each city. prop.test was utilized to analyze the estimated proportion unsolved cases and distinguish CI for each city. purrr::map and purrr::map2 were used to generate a tidy pipeline. finally, I use unnest function to pick the target variables, included estimated proportion, confidence interval boundary for each city. 
```{r}
city_plot = 
result %>% 
ggplot(aes(x=fct_reorder(city_state,estimate), y=estimate))+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high))+
  labs(
    title = "estimated proportion and CI of unsolved cases in each city",
    x = "city state") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
city_plot

```
This plot visualize the estimates and CIs for each city with error bar based on the upper and lower limits with ascending order. 


## Problem 3

First, I build a simulation t-test function for each input true_mean. 
to obtain the estimate and p-value, broom::tidy was utilized to clean the output of t.test.
```{r}
library(tidyverse)
sim_t_test=function(true_mean){
  sample=rnorm(30,mean=true_mean,sd=5)
test_results=t.test(sample,conf.level=0.95)
test_results%>%
  broom::tidy()%>%
  select(estimate,p.value)
}
```
set mean=0, generate 5000 datasets from the Normal distribution model with alpha=0.05
```{r}
sim_reuslt_df_0=
  expand_grid(
    true_mean=0,
    iter=1:5000
  )%>%
  mutate(
    estimate=map(true_mean,sim_t_test)
  )%>%
  unnest(estimate)
head(sim_reuslt_df_0)
```
repeat the above for mean=1,2,3,4,5,6
```{r}

sim_results_df = 
  expand_grid(
    true_mean=1:6,
    iteration=1:5000
  ) %>% 
  mutate(
    estimate_df = map(true_mean,sim_t_test)
  ) %>% 
  unnest(estimate_df)

```


```{r}

summary = sim_results_df %>% 
  group_by(true_mean)%>%
  summarize(
    total = n(),
    reject = sum(p.value < 0.05)
  ) %>% 
  mutate(
    power = reject / total
  )
summary
```
Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
```{r}
summary%>%
  ggplot(aes(x=true_mean,y=power))+
  geom_point()+
  geom_line()+
  labs(title="power vs. true mean",
       x="true mean",
       y="power")
```
as the true mean increasing from 1 to 6, the power also increased from 0.2 to 1.0

```{r}
# average estimate of mean vs true mean
plot2=
  sim_results_df%>%
  group_by(true_mean)%>%
  mutate(estimated_mean=mean(estimate))%>%
  ggplot(aes(x=true_mean,y=estimated_mean))+
  geom_point()+
  geom_line()+
  labs(title="estimated mean vs. true mean",
         x="true mean",
         y="estimated mean")
 plot2 
```

```{r}
plot3=
  sim_results_df%>%
  filter(p.value<0.05)%>%
  group_by(true_mean)%>%
  mutate(estimated_mean=mean(estimate))%>%
  ggplot(aes(x=true_mean,y=estimated_mean))+
  geom_point()+
  geom_line()+
  labs(title="estimated mean vs. true mean(only in samples for which the null was rejected)",
         x="true mean",
         y="estimated mean")
 plot3 
```

