---
title: "p8105_hw5_sk5152"
author: "Shuting Kang"
date: "2022-11-15"
output: github_document
---
## Problem 2

The homicide datasets in 50 large U.S. cities from Washington Post are loaded in this project. 
```{r}
#for loop (map are better actually)
library(tidyverse)
homicide<-read_csv("./data/homicide-data.csv")
head(homicide)
skimr::skim(homicide)
```
```{r}
homicide_CityState<- homicide%>%
  mutate(city_state=str_c(city,state,sep=","))
head(homicide_CityState)

```
The homicides dataset contained `r nrow(homicide)` observation and `r ncol(homicide)` variables
```{r}
summary<-homicide_CityState%>%
  group_by(city_state)%>%
  summarize(
    total_cases=n(),
    solved=sum(disposition=="Closed by arrest"),
    unsolved=sum(disposition!="Closed by arrest")
  )
summary
```
For the city of Baltimore, MD, prop.test function was utilized to estimate the proportion of homicides that are unsolved. broom::tidy was applied to save the output of prop.test as an R object.
```{r}
baltimore<-
  summary%>%
  filter(city_state=="Baltimore,MD")
baltimore
  
  
```
```{r}
baltimore = homicide_CityState %>% 
  filter(city_state == "Baltimore, MD")
baltimore_summary = 
  baltimore %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )
baltimore_test = prop.test(
  x = baltimore_summary %>% pull(unsolved), 
  n = baltimore_summary %>% pull(n)) 
baltimore_test %>% 
  broom::tidy()
```

```{r}
## problem 3 simulation (lecture  code)
library(tidyverse)
sim_t_test=function(true_mean){
  sample=rnorm(30,mean=0)
test_results=t.test(sample)
test_result%>%
  broom::tidy()
}

expand_grid(
  true_mean=0:6,
  iter=1:5
)



sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:100
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

